\documentclass[xcolor=table]{beamer}

\usepackage{lscape, amsmath, amsfonts, amssymb, setspace, theorem, wrapfig, graphicx, float, multirow, subfig, color, rotating, multicol, datetime, natbib, venndiagram, pstricks, xkeyval, tikz, etoolbox, url, hyperref, nth}

\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage[english]{babel}

\title{GV217 - Conflict Analysis}
\subtitle{University of Essex - Department of Government}
\date{Week 18 -- 31 January, 2020}				% or you can specify a date, just write it down instead of "\today"
\author{Lorenzo Crippa} 

\usetheme[progressbar=frametitle]{metropolis}
\usecolortheme{seahorse}						% try others: wolverine; crane...

\begin{document}
\frame{
\titlepage
}

\frame{
\frametitle{What are we doing today?}
Today's topics:
\begin{enumerate}
\item Trends in violence
\item Terrorism
\end{enumerate}
}

\section{Trends in violence}

\frame{
\frametitle{Trends in violence}
\begin{itemize}
\item Do you think we live in a less violent world? In absolute or relative terms? Why? \pause \\ \textcolor{red}{There are differences between absolute and relative numbers!} \pause
\item Are people inherently prone to use violence? \pause
\item What is the role of the international system and power balance? \pause
\item Can ``institutions'' be our savior? Governments, IOs etc. \pause
\item What role will new trends in climate change, technology and alike play in the future?
\end{itemize}
}

\section{Terrorism}

\frame{
\frametitle{What should a definition include?}
What elements should a definition of terrorism include? \pause
\begin{itemize}
\item Violence \pause
\item By non-state actors \pause
\item To achieve political or social goals \pause
\item Through the intimidation of a wide audience \pause
\item By targeting civilians or non-combatants
\end{itemize}
}

\frame{
\frametitle{Group activity}
The rest of the class will be a discussion organised in groups.

Let's divide the class in two groups. You will have a few minutes to discuss the questions in \textcolor{red}{red} and then discuss with the other group.
}

\frame{
\frametitle{An example of a definition}
Fortna (2015) Definition: Terrorists are ``those who employ a systematic campaign of indiscriminate violence against public civilian targets to influence a wider audience. The ultimate aim of this type of violence is to coerce the government to make political concessions'' \pause

\textcolor{red}{Is this definition missing anything?}
}

\frame{
\frametitle{Example 1}
On 3 February 2018 Luca Traini, an Italian white man, targeted black migrants as he drove around the city of Macerata, firing on nationals from Ghana, Mali and Nigeria. He later abandoned his car and made a fascist salute, an Italian flag draped over his shoulders, as police arrested him \\ The shootings came a month before national elections that were marked by furious debate over the influx of some 600,000 mainly African migrants into Italy since 2014 \\ Traini had been an unsuccessful candidate for the anti-immigrant Northern League party and had previously been associated with neo-fascist groups.\pause

\textcolor{red}{Is this terrorism?}
}


\frame{
\frametitle{Example 2}
On the night of October 1, 2017, a gunman opened fire on a crowd of concertgoers at the Route 91 Harvest music festival on the Las Vegas Strip in Nevada. \\ Perpetrator Stephen Paddock, 64, of Mesquite, Nevada, fired more than 1,100 rounds from his suite on the 32nd floor of the nearby Mandalay Bay hotel, killing 58 people and leaving 851 injured, over 400 of them by gunfire and hundreds more in the ensuing panic. \\ The shooting occurred between 10:05 and 10:15 p.m. PDT; about an hour later Paddock was found dead in his room from a self-inflicted gunshot wound. His motive remains unknown. \pause

\textcolor{red}{Is this terrorism?}
}

\frame{
\frametitle{Example 3}
24/01/2006: Assailants raided Demsare village, Adamawa state, Nigeria. This was one of six attacks on villages carried out by the same assailants. \\ At least 15 people were killed across all six events. \\ No group claimed responsibility for the incidents; however, sources attributed the attacks to Fulani militants or Boko Haram. \pause

\textcolor{red}{Is this terrorism?}
}

\frame{
\frametitle{Example 4}
21/12/2017: Assailants attacked the Union of Thessaloniki Daily Newspaper Editors office along Stratigou Kallari Street in Thessaloniki, Central Macedonia, Greece. \\ There were no reported casualties in the incident. \\ The Minorities of Metropolitan Attacks claimed responsibility for the attack. \pause

\textcolor{red}{Is this terrorism?}
}

\frame{
\frametitle{Example 5}
On 20 May 2015, IS conquered the city of Palmyra after intense fighting between IS and Syrian state forces. \\ In the weeks that followed, IS destroyed many ancient monuments and cultural artefacts. \pause

\textcolor{red}{Is this terrorism?}
}

\frame{
\frametitle{Example 6}
On 23 May 1992, Cosa Nostra (the Sicilian branch of Mafia) blew up judge Giovanni Falcone's car, killing the magistrate, his wife and three police escort agents. The bombing took place after courts had confirmed the claims from the so-called ``Maxi Trial'' that had targeted prominent personalities of the Italian Mafia. The killing was part of a long series of violent attacks that followed a wave of prosecution and arrests of leading gangsters, which was facilitated by the adoption of new legal instruments. \pause

\textcolor{red}{Is this terrorism?}
}

%\frame{
%\frametitle{Why use terrorist tactics?}
%\begin{itemize}
%\item Strength/weakness
%	\begin{itemize}
%	\item[--] Do the two core readings agree? Why?
%	\end{itemize}
%\item Ideology-audience
%\item Democracy
%\end{itemize} \pause
%
%Do terrorists win?
%}

\frame{
\frametitle{Conclusion}
\begin{center}
All clear? More questions? \\
See you next week!
\end{center}
}


\end{document}
